---
title: "AE 04"
subtitle: "Airbnbs in Edinburgh"
date: "Due: August 28, 11:59PM"
author: "YOUR NAME GOES HERE"
output: 
  html_document: 
    toc: TRUE
    toc_float: TRUE
    fig_height: 4
    fig_width: 9
---

```{r load-packages, warning = FALSE, message = FALSE}
library(tidyverse)
```

## Clone a repo + start a new project

- Click on the link provided in the slides to create your own private repo for 
this exercise.

- Go to the `ae-04-edinburgh-your-name-here` repo on GitHub that you created

- Click on the green **Code** button, **Use HTTPS**, and click on the clipboard 
icon to copy the repo URL.

- Go to RStudio and go to *File* $\rightarrow$ *New Project* $\rightarrow$ 
*Version Control* $\rightarrow$ *Git, then paste the URL or your assignment
repo into the dialog box *Repository URL*.

- Browse to an appropriate place (perhaps creating a new folder if desired) on
the virtual machine for a folder to be created that contains the AE materials.

- Click *Create Project*, and log in using your GitHub credentials. If you have
successfully logged in, the files from your repo will be displayed in the 
*Files* pane.

- Configure git by typing the following in the Console (using your GitHub
username and e-mail as appropriate)

```{r eval=FALSE}
library(usethis)
use_git_config(user.name="your name", user.email="your email")
```

**RStudio and GitHub can now communicate with each other and you are ready to do the exercise!**

## Practice with ggplot

The data contains information about Airbnb listings in Edinburgh, Scotland. The 
data originally come from [Kaggle](https://www.kaggle.com/thoroc/edinburgh-inside-airbnb/version/2), 
and it has been modified for this exercise. 

Use the code below to load the data from the .csv file. 

```{r load-data}
edibnb <- read_csv("data/edibnb.csv")
```

**Knit this document**. You may see that there is a message beneath the code
used to import the dataset. If you wish to suppress this message, then you may
include `message = FALSE` as an R code chunk option. Modify the code chunk to
do this, and then knit again.

The dataset you’ll be using is called `edibnb`. Run `View(edibnb)` in the 
**Console** to view the data in the data viewer. What does each row in the 
dataset represent?

The `edibnb` data set set has `r nrow(edibnb)` observations (rows).

1. How many columns (variables) does the dataset have? Instead of hard coding 
the number in your answer, use the function `ncol()` to write your answer in 
inline code. 

*Hint: Use the statement above as a guide. What happens when it is knit?*

Knit to see the updates.

2. Fill in the code below to create a histogram to display the distribution of 
`price`.  Once you have modified the code, remove the option `eval = FALSE` from 
the code chunk header. Knit again to see the updates.

```{r plot-price, eval = FALSE}
ggplot(data = ___, mapping = aes(x = ___)) +
  geom_histogram()
```

3. What does the `eval = FALSE` R chunk option do?

Now let's look at the distribution of price for each neighborhood. To do so, we 
will make a faceted histogram where each facet represents a neighborhood and 
displays the distribution of price for that neighborhood.

4. Fill in the code below to create the faceted histogram with informative 
labels. Once you have modified the code, remove the option `eval = FALSE` from 
the code chunk header. Knit again to see the updates.

*Hint: Run `names(edibnb)` in the <b>console</b> to get a list of variable*
*names. Note how the variable for neighborhood is spelled in the data set.*

```{r plot-price-facet, eval = FALSE}
ggplot(data = ___, mapping = aes(x = ___)) +
  geom_histogram() +
  facet_wrap(~___) +
  labs(x = "______", 
      title = "_______", 
      subtitle = "Faceted by ______")
```


5. How would you describe the distribution of price in general? How do 
neighborhoods compare to each other in terms of price?

## Stage, commit, and push

1. If you made any changes since the last knit, knit again to get the final 
version of the AE. 

2. Check the box next to each document in the Git tab (this is called "staging" 
the changes).  Commit the changes you made using an simple and informative 
message.

2. Use the **green arrow** to push your changes to your repo on GitHub.

3. Check your repo on GitHub and see the updated files.

## Resources 

- [ggplot2 reference page](https://ggplot2.tidyverse.org/reference/geom_histogram.html) 
- [ggplot2 cheat sheet](https://rstudio.com/wp-content/uploads/2015/03/ggplot2-cheatsheet.pdf)


<br><br>

<hr> 

*This exercise was modified from Hotels in Edinburgh in [Data Science in Box](https://datasciencebox.org/).*